---
title: "An Overview of `bmisc`: Balamuta Miscellaneousness"
author: "James Balamuta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Overview of bmisc: Balamuta Miscellaneousness}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Intro

The package contains different functions that I have found useful throughout
my time working with _R_. Whether they are beneficial to you, or want you to
pull out your hair, I'll leave that up to you and the issue tracker.

With this being said, to use the package, first install it via either CRAN or
GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("coatless/bmisc@*release")
install.packages("bmisc")
```

Then load it via:

```{r}
library("bmisc")
```

You may wish at times to use functions within this package that collide with similarly named functions in other packages. To do so, please prefix function 
calls by `bmisc::` or `bmisc:::` if the function is not exported.

# Utilities

The package hosts various utilities to improve working with simulated data.

In particular, the package offers the ability to cast a simulation `matrix` to
`data.frame` for graphing within `ggplot2`. The simulation cast feature is
meant to ease the use of simulated data within `ggplot2`. Thus, support exists
for both casting simulated data stored by row (default) and by column into a
`Round` and `Draw` framework, where `Round` means the simulation iteration and
`Draw` means the statistic observed.

```{r simulation_objects}
# Set Seed
set.seed(5812)

# Generate data
m = matrix(rnorm(10), 2, 5)

# Organize by row
wide_m = sim_df(m)

# View first 5 rows
head(wide_m, n = 5)

# Organize by column
long_m = sim_df(m, wide = FALSE)

# View first 5 rows
head(long_m, n = 5)

# Graph wide
autoplot(wide_m)

# Graph long
autoplot(long_m)
```
